Solar wind discontinuities spatial evolution in the outer heliosphere

### 2024-01-30 index.qmd
update

---
title: Solar wind discontinuities spatial evolution
author:
  - name: Zijin Zhang
    email: zijin@ucla.edu
    orcid: 0000-0002-9968-067X
    affiliation: University of California, Los Angeles
    roles: writing
    corresponding: true
  - name: Anton V. Artemyev
    email: aartemyev@igpp.ucla.edu
    orcid: 0000-0001-8823-4474
    affiliation: University of California, Los Angeles
  - name: Vassilis Angelopoulos
    orcid: 0000-0001-7024-1561
    affiliation: University of California, Los Angeles
  - name: Shi Chen
    orcid: 0000-0002-2582-7085
    affiliation: University of California, Los Angeles
affiliations:
  - id: ucla
    name: University of California, Los Angeles
execute: 
  eval: false
code-links:
  - repo
  - href: https://app.tana.inc?nodeid=Kmdzbyj-36NM
    text: Tana
---

@@

::: {#fig-ids_examples .column-page layout-ncol="2"}
![Current sheets in the heliosheath: Voyager 1, 2009](images/jgra21162-fig-0009.png){fig-alt="Hodograms produced by means of a minimum variance analysis for the current sheets associated with the sector boundaries in Figures 8 and 10. (b, d, and f) The value of the component of B along the minimum variance direction (Bm) as a function of time, N. (a, c, and e) The components of B along the intermediate variance direction (Bi) and maximum variance direction (BM)."}

@@

Discontinuities examples across the heliosphere
:::

@sodingRadialLatitudinalDependencies2001 studied the radial distribution of discontinuities in the solar wind between 0.3 and 19 AU during solar activity minimum. @liuCharacteristicsInterplanetaryDiscontinuities2021 studied the spatial evolution of the discontinuities from 0.13-0.9 AU, using measurements from the Parker Solar Probe. [Typical rate of occurrence is about 50 per day at 1AU]{.aside}

@@

Spatial distribution of the discontinuities
:::

>>>>

---
title: Solar wind discontinuities spatial evolution in the outer heliosphere
author:
  - name: Zijin Zhang
    email: zijin@ucla.edu
    orcid: 0000-0002-9968-067X
    affiliation: University of California, Los Angeles
    roles: writing
    corresponding: true
  - name: Anton V. Artemyev
    email: aartemyev@igpp.ucla.edu
    orcid: 0000-0001-8823-4474
    affiliation: University of California, Los Angeles
  - name: Vassilis Angelopoulos
    orcid: 0000-0001-7024-1561
    affiliation: University of California, Los Angeles
  - name: Shi Chen
    orcid: 0000-0002-2582-7085
    affiliation: University of California, Los Angeles
affiliations:
  - id: ucla
    name: University of California, Los Angeles
execute: 
  eval: false
code-links:
  - repo
  - href: https://app.tana.inc?nodeid=Kmdzbyj-36NM
    text: Tana
  - href: https://www.overleaf.com/project/65b0a9c80a3616adf6e599e8
    text: Overleaf
---

@@

::: {.content-visible when-format="html"}
::: {#fig-ids_examples .column-page layout-ncol="2"}
![Current sheets in the heliosheath: Voyager 1, 2009](images/jgra21162-fig-0009.png){fig-alt="Hodograms produced by means of a minimum variance analysis for the current sheets associated with the sector boundaries in Figures 8 and 10. (b, d, and f) The value of the component of B along the minimum variance direction (Bm) as a function of time, N. (a, c, and e) The components of B along the intermediate variance direction (Bi) and maximum variance direction (BM)."}

@@

Discontinuities examples across the heliosphere
:::
:::

@sodingRadialLatitudinalDependencies2001 studied the radial distribution of discontinuities in the solar wind between 0.3 and 19 AU during solar activity minimum. @liuCharacteristicsInterplanetaryDiscontinuities2021 studied the spatial evolution of the discontinuities from 0.13-0.9 AU, using measurements from the Parker Solar Probe.

::: {.content-visible when-format="html"}

[Typical rate of occurrence is about 50 per day at 1AU]{.aside}

@@

Spatial distribution of the discontinuities
:::
:::
